\printbibliography[title={Список использованных источников}]

\addcontentsline{toc}{chapter}{Список использованных источников}

\begin{thebibliography}{99}
	
	\bibitem{Awais2022}\label{Awais2022}
	Аваис М., Гу В., Дламини Г., Холматова З., Суччи Дж.  
	An experience in automatically extracting CAPAs from code repositories // arXiv.org. 2022.  
	URL: \url{https://arxiv.org/pdf/2212.09910}
	
	\bibitem{Bugayenko2022}\label{Bugayenko2022}
	Bugayenko Y., Daniakin K., Farina M., Jolha F., и др.  
	Extracting corrective actions from code repositories //  
	В сб.: Proceedings of the 19th International Conference on Mining Software Repositories (MSR 2022). ACM, 2022.  
	DOI: \url{https://dl.acm.org/doi/abs/10.1145/3524842.3528517}
	
	\bibitem{Holmatova2021}\label{Holmatova2021}
	Холматова З., Педрич В., Суччи Д.  
	A meta-analytical comparison of Naive Bayes and Random Forest for software defect prediction // 
	URL: \url{https://link.springer.com/chapter/10.1007/978-3-031-35501-1_14#citeas}
	
	\bibitem{Zenodo2025}\label{Zenodo2025}
	Examining the Success of an Open Source Software Project Analysing Its Repository //  
	Zenodo. 2025.  
	DOI: \url{https://doi.org/10.5281/zenodo.10046579}
	
	\bibitem{DiBella2014}\label{DiBella2014}
	Di Bella E., Tamburri D.A., Serebrenik A., Storey M.-A., Melegati J., Ferreira M.  
	GitHub Projects: Quality Analysis of Open-Source Software //  
	В сб.: Proceedings of the 10th International Conference on Open Source Systems.  
	Cham: Springer, 2014. С. 159–169.  
	URL: \url{https://link.springer.com/chapter/10.1007/978-3-319-13734-6_6}
	
	\bibitem{Utkin2020}\label{Utkin2020}
	Utkin L. V.  
	An imprecise deep forest for classification // Expert Systems with Applications.  
	2020. Т. 141. С. 112978.  
	URL: \url{https://www.sciencedirect.com/science/article/pii/S0957417419306967}
	
	\bibitem{Jain2020}\label{Jain2020}
	Jain A. K., Murty M. N., Flynn P. J.  
	The k-means Algorithm: A Comprehensive Survey and Performance Evaluation //  
	Electronics. 2020. Т. 9, № 8.  
	DOI: \url{https://www.mdpi.com/2079-9292/9/8/1295}
	
	\bibitem{Picha2019}\label{Picha2019}
	Pícha P.  
	Detecting software development process patterns in project data //  
	В кн.: Proceedings of the 23rd International Conference on Soft Computing MENDEL 2019.  
	Brno: Springer, 2019.  
	URL: \url{https://otik.uk.zcu.cz/handle/11025/37196}
	
	\bibitem{GithubAPI}\label{GithubAPI}
	Github API documentation.  
	URL: \url{https://docs.github.com/en/rest?apiVersion=2022-11-28}
	
	\bibitem{PyGithub}\label{PyGithub}
	PyGithub documentation.  
	URL: \url{https://pygithub.readthedocs.io/en/stable/}
	
	\bibitem{FDA}\label{FDA}
	FDA — Corrective and Preventive Actions (CAPA).  
	URL: \url{https://www.fda.gov/inspections-compliance-enforcement-and-criminal-investigations/inspection-guides/corrective-and-preventive-actions-capa}
	
	\bibitem{One-Class}\label{One-Class}
	Shehab M. A., Khreich W., Hamou-Lhadj A. и др.  
	Commit-Time Defect Prediction Using One-Class Classification. 2024.  
	URL: \url{https://users.encs.concordia.ca/~abdelw/papers/JSS24-OCC_preprint.pdf}
	
	\bibitem{Commit-classification}\label{Commit-classification}
	Heričko T., Šumak B.  
	Commit Classification Into Software Maintenance Activities: A Systematic Literature Review. 2023.  
	URL: \url{https://www.researchgate.net/profile/Samesun-Singh/post/I_need_a_question_depending_on_PICO_frame_work_related_to_operating_system_can_anyone_suggest_me/attachment/64ef8b7e806fe2503d067dd1/AS%3A11431281184732300%401693420414326/download/Heri%C4%8Dko_COMPSAC23_paper-1.pdf}
	
	\bibitem{Hericko}\label{Hericko}
	Heričko T., Brdnik S., Šumak B. Commit Classification Into Maintenance Activities Using Aggregated Semantic Word Embeddings of Software Change Messages // SQAMIA 2022: Workshop on Software Quality, Analysis, Monitoring, Improvement, and Applications, Novi Sad, Serbia, September 11–14, 2022. CEUR Workshop Proceedings, Vol. 3237. URL: \url{https://ceur-ws.org/Vol-3237/paper-her.pdf}
	
	\bibitem{Sazid}\label{Sazid}
	Sazid Y., Kuri S., Ahmed K. S., Satter A.  
	Commit Classification into Maintenance Activities Using In-Context Learning Capabilities of Large Language Models. 2024.  
	URL: \url{https://www.scitepress.org/Papers/2024/126867/126867.pdf}
	
	\bibitem{MasterControl}\label{MasterControl}
	MasterControl CAPA service. URL: \url{https://www.mastercontrol.com/quality/capa-software/management/}
	
\end{thebibliography}
